Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-07-26 ms.tex
Spelling

In order to estimate the \ac{ML} estimator accuracy for a matched filter, we will momentarily consider the likelihood for a single detector, and surpress the intrinsic degrees of freedom:
%
\begin{equation}\label{eq:gaussian-likelihood}
	\fl\mathcal{L}(x_i; \rho_i, \gamma_i, \tau_i) = p(x_i | \rho_i, \gamma_i, \tau_i)
		\propto \exp \left[
		- \frac{1}{2} \int_0^\infty \frac{\left|x_i (\omega)
			- h_i(\omega; \rho_i, \gamma_i, \tau_i) \right|^2}{S_i(\omega)} \, \mathrm{d}\omega
	\right],
\end{equation}
%
with $h_i(\omega; \rho_i, \gamma_i, \tau_i)$ given by \Eref{eq:signal-model}.

>>>>

In order to estimate the \ac{ML} estimator accuracy for a matched filter, we will momentarily consider the likelihood for a single detector, and suppress the intrinsic degrees of freedom:
%
\begin{equation}\label{eq:gaussian-likelihood}
	\fl\mathcal{L}(x_i; \rho_i, \gamma_i, \tau_i) = p(x_i | \rho_i, \gamma_i, \tau_i)
		\propto \exp \left[
		- \frac{1}{2} \int_0^\infty \frac{\left|x_i (\omega)
			- h_i(\omega; \rho_i, \gamma_i, \tau_i) \right|^2}{S_i(\omega)} \, \mathrm{d}\omega
	\right],
\end{equation}
%
with $h_i(\omega; \rho_i, \gamma_i, \tau_i)$ given by \Eref{eq:signal-model}.
